Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-11 WSSSPE1_report/WSSSPE1_summary_report.tex
minor format and added some content to use-case section

>>>>

The software projects discussed in the workshop can be classified as follows:

- General Purpose
    Software that enables other software to run by providing suitable environment. eg. Collaborative development, Workflow and scripting frameworks

- Special Purpose
Software that was developed specifically for a target use-case scenario or keeping some fixed requirements in mind.

--Science Oriented
      Software developed to solve domain science problems eg. MINRES/QLP

--Infrastructure Oriented
      Software developed to better utilize new infrastructure, eg. MVAPICH
